---
title: "Chapter 4 RealWorld Application of FH for B subgroup"
author: "David B"
output: 
  word_document:
    toc: yes
---

### Install/Load packages
```{r, message=FALSE, warning=FALSE}
if(!require(tidyverse)) install.packages("tidyverse", 
                                         repos = "http://cran.us.r-project.org")
if(!require(EdSurvey)) install.packages("EdSurvey", 
                                         repos = "http://cran.us.r-project.org")
if(!require(sae)) install.packages("sae", 
                                         repos = "http://cran.us.r-project.org")
```

### Import & Wrangle Administrative Data for B subgroup

**FER variable**

Composite measure of a state’s median household income and wealth (Family Economic Resources; “FER”)

The income data come from page 3 of the following document on the US Census website:
https://www.census.gov/content/dam/Census/library/publications/2017/acs/acsbr16-02.pdf

The wealth data come from page 9 of the following document on the US Census website:
https://www.census.gov/content/dam/Census/library/working-papers/2017/demo/FY2016-129.pdf

```{r, warning=FALSE, message=FALSE}

#First estabish a column for state abbreviations
State <- read_csv("[pathfile]/2+.csv")
State <- State[,1]

med_income <- c(45182, 74165, 52062, 42530, 65087, 64598, 72121, 61882, 49852, 51753, 74451, 48728, 60094, 50896, 55172, 54520, 45541, 46106, 52111, 76596, 71146, 51584, 64188, 40910, 50642, 49924, 55474, 53320, 70813, 73242, 45710, 61311, 48420, 60944, 51610, 49062, 54748, 56207, 58826, 47790, 53746, 47818, 56139,
63794, 57565, 66916, 64764, 42620, 56115, 60570)

med_wealth <- c(83349, 120365, 79785, 78554, 96190, 118180, 147278, 126219, 88938, 78710, 153570, 95389,
102768, 90247, 108512, 96608, 87998, 86574, 115971, 136853, 148838, 87983, 133224, 75772, 91123, 112580,
96347, 63224, 148468, 143831, 88135, 100543, 93956, 103615, 87717, 82256, 93621, 113131, 108967, 93925,
99726, 87508, 78825, 104950, 141716, 119459, 106626, 92262, 111986, 119763)

med_income <- as.data.frame(med_income)
med_wealth <- as.data.frame(med_wealth)

#bind
demographic_df <- cbind(State, med_income, med_wealth)

#create composite variable (FER)
demographic_df$FER <- (demographic_df$med_income + demographic_df$med_wealth)/2

#remove redundancies
demographic_df <- dplyr::select(demographic_df, "State", "FER")

#cleanup environment
rm(med_income, med_wealth, State)

```

**SQI variable**

The variable, SQI, is measured on a continuous scale with scores ranging 0.0 to 100.0, and reflects the average of states’ “Chance for Success” and “School Finance” ratings. The Chance for Success rating is meant to capture lifelong learning opportunities for students—beginning with early childhood, and progressing through K-12 education into adulthood. The School Finance rating is based on school spending patterns as well as how education dollars are distributed across each state (Education Week Research Center, 2015).

The data are gathered from the following website:

https://www.edweek.org/ew/qc/2015/2015-state-report-cards-map.html?intc=EW-QC15-LFTNAV


NB: Hawaii is a single-district jurisdiction. As a result, it is not possible to calculate measures of financial equity, which capture the distribution of funding across districts within a state. Thus Hawaii does not receive a *composite* grade for school finance. Instead, its "Spending" score takes the place of school finance, which is one of the sub-components of the overall school finance measure in other states. 

```{r message=FALSE, warning=FALSE}

chance_for_success <- c(71.2, 76.2, 71.2, 71.0, 72.8, 83.4, 87.5, 78.5, 75.5, 74.3, 80.0, 74.2, 80.1, 76.8, 84.1, 82.7, 75.3, 69.9, 80.0, 85.8, 91.9, 76.1, 87.3, 68.5, 77.4, 77.0, 83.7, 65.6, 89.6, 87.6, 67.2, 80.9, 76.2, 87.5, 76.6, 72.0, 74.8, 82.6, 79.7, 73.3, 78.9, 73.1, 73.4, 80.5, 85.7, 84.9, 80.0, 70.3, 82.6, 82.5)

school_finance <- c(69.7, 81.7, 65.1, 73.1, 67.0, 68.8, 87.1, 83.2, 68.9, 71.2, 81.9, 59.1, 78.7, 73.3, 73.9, 75.5, 73.5, 75.8, 78.7, 86.8, 83.0, 74.6, 75.7, 66.9, 70.7, 71.7, 75.4, 62.8, 78.6, 86.8, 69.0, 88.8, 66.5, 74.3, 76.7, 66.6, 68.9, 82.2, 86.5, 70.8, 66.6, 68.4, 65.5, 61.7, 86.1, 76.9, 71.8, 89.2, 82.0, 89.3)

#bind
predictors_df <- cbind(demographic_df, chance_for_success, school_finance)

#correct names of last two variables
names(predictors_df) <- c("State", "FER", "chance_for_success", "school_finance")

#Create SQI variable
predictors_df$SQI <- (predictors_df$chance_for_success + predictors_df$school_finance)/2

#remove irrelevant variables from df
predictors_df <- dplyr::select(predictors_df, State, FER, SQI)

#cleanup environment
rm(demographic_df, chance_for_success, school_finance)

```

**%BA variable**

This variable is operationalized as the percent of adults (25 and older) by state that have earned a bachelor’s or more advanced degree (%BA). 

Data are collected from the American Community Survey. Specifically, the following website:

https://data.census.gov/cedsci/table?d=ACS%205-Year%20Estimates%20Data%20Profiles&table=DP02&tid=ACSDP5Y2015.DP02&y=2015&g=0400000US39,32,31,78,34,33,36,35,38,37,72,30,29,28,21,20,23,22,66,69,25,24,27,26,60,18,17,19,54,10,53,56,12,55,13,16,15,50,51,06,09,08,42,45,44,47,46,05,49,04,48,41,40,02_0100000US&hidePreview=true&t=Educational%20Attainment&tp=true&moe=true

Note to self: Insert limitation bullet in proposal
```{r, warning=FALSE, message=FALSE}

#Import
Percent_BAplus_df <- read_csv("[pathfile]/Percent_BAplus_df.csv")


#Merge in %BA variable
predictors_df <- inner_join(predictors_df, Percent_BAplus_df, by = "State")

#cleanup environment
rm(Percent_BAplus_df)

```

**%AA variable**

Gathered from the American Community Survey (ACS), a program of the US Census. Specifically, from this website--
https://data.census.gov/cedsci/table?t=004%20-%20Black%20or%20African%20American%20alone&tid=ACSSPP1Y2015.S0201&hidePreview=true&g=0400000US02,04,05,06,08,09,10,12,13,15,16,17,18,19,20,21,22,23,24,26,25,27,28,29,31,30,32,33,34,35,36,37,38,39,40,41,42,44,46,01,45,47,48,49,51,50,53,54,55,56&moe=false&tp=true

The data are filtered for the "Black of African American" population across across states. 

NB: This metric for 2015 (1-year estimate), is not available for 12/50 states. The data are simply missing in the ACS data set.
These states are the following: AK, HI, ID, ME, MT, NH, NM, ND, SD, UT, VT, & WY. These are states in which the prevalence of Black residents is relatively low.

Instead, "5-year" estimates are used for these states. Estimates based on pooling data for these jurisdictions across multiple years. Specifically, from this website--
https://data.census.gov/cedsci/table?tid=ACSDT5Y2015.B05003B&t=Race%20and%20Ethnicity&vintage=2015&g=0400000US02,15,16,23,30,33,35,38,46,49,50,56&hidePreview=true&tp=false


NB: This variable represents an estimate of the proportion of the Black population in each state born in the US. 
```{r message=FALSE, warning=FALSE}

#Import data
Black_df_from_Census <- read_csv("[pathfile]/Black_df_from_Census.csv")

#Change from propotion to percent
Black_df_from_Census$AA <- Black_df_from_Census$AA*100

#Bind AA variable
predictors_df <- cbind(predictors_df, Black_df_from_Census$AA)

#correct variable names
names(predictors_df) <- c("State", "FER", "SQI", "p_BA", "AA")

#Clean up environment
rm(Black_df_from_Census)

```

**Tidy up predictors dataset**
```{r}

#Make sure all values are rounded to the nearest tenth (one decimal)
predictors_df$AA <- format(round(predictors_df$AA), nsmall=1)

#make sure all predictor variables are numeric
predictors_df[, 2:5] <- apply(predictors_df[, 2:5], 2, as.numeric)

```

### Combine direct estimate data and state-level predictors

```{r warning=FALSE, message=FALSE}

#import B_DEs
B_DEs <- read_csv("[pathfile]/B_DEs.csv")
B_DEs <- B_DEs[,-1]

FH_B_df <- full_join(B_DEs, predictors_df, by = "State")

#make sure merged dataset is 50 rows long

```


### Merge NAEP reported estimates of mean math achievent (for B) into the data set
```{r warning=FALSE, message=FALSE}

#Import the NAEP-reported means and standard errors for target values
NR_TV_Mean_SE <- read_csv("[pathfile]/NR_TV_Mean_SE.csv")

NR_TV_B_MEAN_SE <- dplyr::select(NR_TV_Mean_SE, "State", "NR_B_Mean", "NR_B_SE")

#use full join
FH_B_df <- full_join(FH_B_df, NR_TV_B_MEAN_SE, by = "State")

#verify that are still only 50 rows

#Export (save) FH_df
write.csv(FH_B_df, "[pathfile]/FH_B_df.csv")

```

**Free up memory**
```{r warning=FALSE, message=FALSE}
rm(list = ls())
```

### Execute FH

Import data set and combine DEs
```{r warning=FALSE, message=FALSE}
FH_B_df <- read_csv("[pathfile]/FH_B_df.csv")
FH_B_df <- FH_B_df[,-1]

FH_B_df <- FH_B_df %>%
  unite("de", B_direct_est, NR_B_Mean, na.rm=T)

FH_B_df <- FH_B_df %>%
  unite("se", B_se, NR_B_SE, na.rm=T)         

```

```{r warning=FALSE, message=FALSE}

options(digits = 5)

FH_B_df$de <- as.numeric(FH_B_df$de)
FH_B_df$se <- as.numeric(FH_B_df$se)

attach(FH_B_df)
B_RW_FH_results <- mseFH(de ~ p_BA + FER + SQI + AA, se^2)

FH_B_df$eblup <- B_RW_FH_results[["est"]][["eblup"]]
FH_B_df$eblup_mse <- B_RW_FH_results[["mse"]]
FH_B_df$eblup_se <- sqrt(FH_B_df$eblup_mse)

FH_B_df$method <- "NAEP"
#HI
FH_B_df[11,11] <- "FH"
#ID
FH_B_df[12,11] <- "FH"
#ME 
FH_B_df[19,11] <- "FH"
#MT 
FH_B_df[26,11] <- "FH"
#NH 
FH_B_df[29,11] <- "FH"
#NM 
FH_B_df[31,11] <- "FH"
#OR 
FH_B_df[37,11] <- "FH"
#SD 
FH_B_df[41,11] <- "FH"
#UT 
FH_B_df[44,11] <- "FH"
#VT 
FH_B_df[45,11] <- "FH"
#WY
FH_B_df[50,11] <- "FH"

#Create final "Mean" and "SE" values (eblups for FH states)
FH_B_df$Mean <- ifelse(FH_B_df$method=="NAEP", FH_B_df$de, FH_B_df$eblup)
FH_B_df$StdErr <- ifelse(FH_B_df$method=="NAEP", FH_B_df$se, FH_B_df$eblup_se)

```

### Create Visualizations of Results

First, descriptive statistics by method
```{r warning=FALSE, message=FALSE}

FH_B_df %>%
  group_by(method) %>%
  summarize(Mean_Est = mean(Mean),
            Median_Est = median(Mean),
            SD = sd(Mean),
            Min = min(Mean),
            Max = max(Mean))

```

Now, visualization
```{r warning=FALSE, message=FALSE,}

FH_B_df$lower_bound <- FH_B_df$Mean - 1.96*FH_B_df$StdErr
FH_B_df$upper_bound <- FH_B_df$Mean + 1.96*FH_B_df$StdErr

FH_B_df <- FH_B_df %>%
  mutate(State = fct_reorder(State, desc(Mean)))

ggplot() + 
  geom_errorbar(data=FH_B_df, mapping=aes(xmin=lower_bound, xmax=upper_bound, y=State, col = method)) + 
  xlab("NAEP score") +
  theme(text=element_text(size=8, family="serif",)) + 
  geom_point(data=FH_B_df, aes(Mean, State), size=0.5) + 
  theme(axis.text.y=element_text(colour=c("black", "red", "black", "black", "black", "black", "red", "black", "black", "black",
                                       "black", "red", "black", "black", "black", "black", "red", "black", "red", "red", 
                                       "red", "black", "black", "red", "black", "black", "black", "red", "red", "black", 
                                       "black", "black", "black", "black", "black", "black", "red", "black", "black", "black", 
                                       "black", "black", "black", "black", "black", "black", "black", "black", "black", "black")))

```


Extra visualization, whereby the differences between states' mean estimates and the mean of all mean estimates for the B subgroup are illustrated and color-coded by technique 
```{r warning=FALSE, message=FALSE}

FH_B_df <- FH_B_df %>%
  mutate(Difference = Mean - mean(Mean))

FH_B_df <- FH_B_df %>%
  mutate(State = fct_reorder(State, desc(Difference)))


ggplot(FH_B_df, aes(x=Difference, y=State, color=method)) +
  geom_point() +
  geom_vline(xintercept = 0) + 
  xlab("Difference from subgroup mean") +
  theme(text=element_text(size=8, family="serif")) + 
  theme(axis.text.y=element_text(colour=c("black", "red", "black", "black", "black", "black", "red", "black", "black", "black",
                                       "black", "red", "black", "black", "black", "black", "red", "black", "red", "red", 
                                       "red", "black", "black", "red", "black", "black", "black", "red", "red", "black", 
                                       "black", "black", "black", "black", "black", "black", "red", "black", "black", "black", 
                                       "black", "black", "black", "black", "black", "black", "black", "black", "black", "black")))


```


Extra visualization to demonstrate that none of the FH estimates of mean achievement are outliers.
```{r warning=FALSE, message=FALSE}

FH_B_df <- FH_B_df %>%
  mutate(State = fct_reorder(State, desc(Mean)))


 FH_B_df %>%
  ggplot(., aes(x=method, y=Mean, color=method)) + 
  geom_dotplot(binwidth = .5, binaxis = "y", stackdir = "center") +
  geom_hline(yintercept = 274, color="black") + 
  geom_hline(yintercept = 245, color="black") + 
  ylab("Score") +
  theme(text=element_text(size=14,  family="serif"))


```

Extra visualization that provides a state-by-state comparison of overall mean achievement (for all students) and mean achievement for Black students (color-coded by method-- NAEP vs FH).

```{r warning=FALSE, message=FALSE}

#Merge in achievement estimates for all_students
All_Students <- read_csv("[pathfile]/All_Students.csv")

FH_B_df <- FH_B_df %>%
  inner_join(All_Students, by = "State")

#Redefine difference
FH_B_df <- FH_B_df %>%
  mutate(Difference = Mean - All_Students)

FH_B_df <- FH_B_df %>%
  mutate(State = fct_reorder(State, desc(Difference)))

ggplot(FH_B_df, aes(x=Difference, y=State, color=method)) +
  geom_point() +
  xlab("Difference from mean for all students in state") +
  theme(text=element_text(size=8, family="serif")) + 
  theme(axis.text.y=element_text(colour=c("red", "black", "red", "black", "black", "black", "black", "black", "black", "black",
                                       "black", "black", "black", "black", "black", "black", "black", "black", "black", "black", 
                                       "black", "black", "black", "red", "black", "black", "black", "red", "red", "black", 
                                       "black", "red", "black", "red", "black", "black", "red", "red", "black", "black", 
                                       "red", "red", "black", "black", "black", "black", "black", "black", "black", "black")))



```


